Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex

For scenarios with multiple shared logs and many clients, co-locating
sequencers on the same physical node is not ideal. Building a
load balancer that can migrate the shared resource (in this case, the resource
that mediates access to the tail of the log) is a time-consuming, non-trivial task that requires building subsystems
for migrating resources, monitoring the workloads, collecting metrics that
describe the utilization on the physical nodes, partitioning resources,
maintaining cache coherence, and managing multiple sequencers. The following
experiments demonstrate the feasibility of using the mechanisms of the
Malacology load balancing interface to inherit all these features and to
alleviate load from overloaded servers with multiple sequencers.

>>>>

For scenarios with multiple shared logs and many clients, co-locating
\paa{you might want a sentence or two of high-level explanation of this use case.
in practice, a storage system implementing CORFU will support a multiplicity of independent
totally-ordered logs (eg, one for each application).}
sequencers on the same physical node is not ideal. Building a
load balancer that can migrate the shared resource (in this case, the resource
that mediates access to the tail of the log) is a time-consuming, non-trivial task that requires building subsystems
for migrating resources, monitoring the workloads, collecting metrics that
describe the utilization on the physical nodes, partitioning resources,
maintaining cache coherence, and managing multiple sequencers. The following
experiments demonstrate the feasibility of using the mechanisms of the
Malacology load balancing interface to inherit all these features and to
alleviate load from overloaded servers with multiple sequencers.
